Try Bayesian Survival Analysis using the JACC study data (Bayesian Survival Analysis presentations)

### 2020-01-13 ForReport20200114/HandOutEngBayes.Rmd
updated things for the slides

---
title: "Try Bayesian Survival Analysis using the JACC study data (Bayesian Survival Analysis presentations)"
subtitle: "Tables and figures for analysing the association between milk intake and stroke mortality."
author: "Chaochen Wang | Aichi Medical University"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
    keep_tex: true
    # includes:  
    #   in_header: preamble-latex.tex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

@@

```{r echo=FALSE, fig.height=4.5, fig.width=5, message=FALSE, warning=FALSE, fig.cap="Traceplot for AFT, and HR of daily milk drinkers from crude model (men)."}
library(tidyverse)
ggSample %>% 
  filter(Iteration >= 120 & Parameter %in% c("beta[5]", "HR[5]", "AFT[5]")) %>% 
  ggs_traceplot()
```
```{r badtrace, echo=FALSE, out.width = '90%', cache=TRUE, fig.cap="Not overlapping traceplot indicating that model is not converged.",fig.align='center', fig.margin = TRUE}
knitr::include_graphics("fig/badtraceplot.png")
```

>>>>

---
title: "Try Bayesian Survival Analysis using the JACC study data (Bayesian Survival Analysis presentations)"
subtitle: "Tables and figures for analysing the association between milk intake and stroke mortality."
author: "Chaochen Wang | Aichi Medical University"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
    keep_tex: true
    # includes:  
    #   in_header: preamble-latex.tex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
editor_options: 
  chunk_output_type: console
---

@@

```{r echo=FALSE, fig.height=4.5, fig.width=5, message=FALSE, warning=FALSE, fig.cap="Traceplot for AFT, and HR of daily milk drinkers from crude model (men)."}
library(tidyverse)
ggSample %>% 
  filter(Iteration >= 120 & Parameter %in% c("beta[5]", "HR[5]", "AFT[5]")) %>% 
  ggs_traceplot()
```

```{r badtrace, echo=FALSE, out.width = '90%', cache=TRUE, fig.cap="Not overlapping traceplot indicating that model is not converged.",fig.align='center', fig.margin = TRUE}
knitr::include_graphics("fig/badtraceplot.png")
```
